Data Predictive Control with Random Forests:\\Theory and Applications

### 2017-12-24 paper/first submission/cs-challenges.tex
first change fot the revision

\textit{Data Availability:} The main practical challenge for DPC lies in the availability of data for training and we require answers to questions like how much data (functional testing) is required, and how should the sampling be done? Therefore, the procedure for optimal experiment design, and model improvement with estimation of variance in predictions is one of the main focus of our ongoing work.

\textit{Stability:} While the buildings are inherently stable, many other applications require stability guarantees. In our ongoing work, we are working towards proving asymptotic stability to origin with DPC-RT and DPC-En by using concept of switched LTI systems. This will make DPC useful for systems with faster dynamics.

\textit{Robustness:} Another direction of work is on handling uncertainties in the DPC framework, namely an extension to Scenario DPC to account for the disturbance uncertainty. This will help us in quantifying the robustness of DPC.

>>>>

\begin{enumerate}
\item \emph{\textbf{Data Availability:}} The main practical challenge for DPC lies in the availability of data for training and we require answers to questions like how much data (functional testing) is required, and how should the sampling be done? Therefore, the procedure for optimal experiment design, and model improvement with estimation of variance in predictions is one of the main focus of our ongoing work.
\item \emph{\textbf{Stability:}} While the buildings are inherently stable, many other applications require stability guarantees. In our ongoing work, we are working towards proving asymptotic stability to origin with DPC-RT and DPC-En by using concept of switched LTI systems. This will make DPC useful for systems with faster dynamics.
\item \emph{\textbf{Robustness:}} Another direction of work is on handling uncertainties in the DPC framework, namely an extension to Scenario DPC to account for the disturbance uncertainty. This will help us in quantifying the robustness of DPC.
\end{enumerate}
